%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Danyal Abbas} \\ \vspace{1pt}
    \small +923073669967 $|$ \href{mailto:abasdaniel61@gmail.com}{\underline{abasdaniel61@gmail.com}} $|$ 
    \href{https://linkedin.com/in/danyalabbas}{\underline{linkedin.com/in/danyalabbas}} $|$
    \href{https://github.com/danyalabbas}{\underline{github.com/DanyalAbbas}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NED University}{Karachi, Sindh}
      {Bachelor of Science in Computer Science And IT}{Aug. 2024 -- May 2028}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Trainee Engineer}{May 2025 -- Present}
      {CloudJunction Advisers}{Karachi, Sindh}
      \resumeItemListStart
       \resumeItem{Sole-developer of the Salesforce-based product \textbf{InvoiceJunction}, responsible for development and maintenance.}
       \resumeItem{Independently managed customer support tickets, implementing scalable solutions and enhancements.}
       \resumeItem{Designed and implemented a Refund Management System by integrating the Stripe API.}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Jr. Python Developer | Jr. ML Engineer}{Sep. 2024 -- Apr. 2025}
      {Devpii Inc}{Karachi, Sindh}
      \resumeItemListStart
        \resumeItem{Developed and deployed deep learning models including CNNs and custom neural networks for image classification and object detection tasks.}
        \resumeItem{Implemented and fine-tuned YOLOv8 for real time object detection in Python using OpenCV.}
        \resumeItem{Built advanced Retrieval-Augmented Generation (RAG) models for intelligent document QA and chatbot applications, leveraging vector databases and LLMs.}
    \resumeItemListEnd

    \resumeSubheading
      {Project-Based Software Dev.}{Feb 2024 -- Jan 2025}
      {DunixStore Inc}{Remote}
      \resumeItemListStart
        \resumeItem{Developed customized POS software solutions for company clients.}
        \resumeItem{Worked on 30+ scripting and automation projects in Python using libraries like Selenium, BeautifulSoup, etc}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Teehee Tutor AI} $|$ \emph{Python, FastAPI,  Langchain, OpenAI, Docker, ChromaDB}}{Apr 2025 -- Apr 2025}
          \resumeItemListStart
            \resumeItem{Achieved 1st place in Urdu AI Datathon (10 days) at Techfest '25, NEDUET as a solo 1st year out of 21 teams of 3-5 seniors.}
            \resumeItem{Applied Advanced RAG techniques like Query Transformation, Reranking, Query Construction, Multi-Query, Rag-Fusion, and many Langchain functions.}
            \resumeItem{Reduced Hallucination Rate from 67.8\% to 4.9\% with an insane accuracy of 95.1\% using open source
LLM Llama 3.1 instant (8B).}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SignSpeak} $|$ \emph{Python, Pygame, Tensorflow, Mediapipe, gTTS}}{Feb 2024 -- Mar 2024}
          \resumeItemListStart
            \resumeItem{Developed a Machine learning software that translated Sign language into English language with an incredible accuracy of 90\% with Text-To-Speech.}
            \resumeItem{Received the best project leader award and was given prizes and applause at Bano Qabil 2.0 and was offered an interview by the Bano Qabil management.}
            \resumeItem{Added Text-To-Speech using Python library gTTS, making it 20\% more user-friendly.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL (Postgres), HTML/CSS, Apex} \\
     \textbf{Frameworks}{: FastAPI, Scikit-learn, Flask, Tensorflow, Keras, Pygame} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, VS Code, Visual Studio, PyCharm} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Seaborn, }
    }}
 \end{itemize}


%-----------CERTIFICATIONS-----------

\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Advanced Learning Algorithms (DeepLearningAI)} \\
        \href{https://www.coursera.org/account/accomplishments/records/GMHDYK93ITDR}{\textcolor{blue}{View Certificate}} \\
        
        \textbf{Supervised Machine Learning: Regression and Classification (DeepLearningAI)} \\
        \href{https://www.coursera.org/account/accomplishments/records/G293FTEQE9C2}{\textcolor{blue}{View Certificate}} \\
        
        \textbf{Python for Data Science, AI \& Development (IBM)} \\
        \href{https://www.coursera.org/account/accomplishments/records/6NZDFEBX2EKS}{\textcolor{blue}{View Certificate}} \\
        
        \textbf{Intermediate Machine Learning (Kaggle Learn)} \\
        \href{https://www.kaggle.com/learn/certification/danyalabbas1/intermediate-machine-learning}{\textcolor{blue}{View Certificate}} \\
    }}
\end{itemize}

 


%-------------------------------------------
\end{document}
